Software Defect Prediction: Review, Commentary, and Future Work

### 2015-12-14 paper/paper.tex
Started on data sources section

@@

\section{Data Sources}

>>>>

Jun Zheng \cite{zheng2010} argued that the mistakenly predicting a module as non-defective is more dangerous and costly than mistakenly predicting a module as defective. He presented three algorithms which boost neural networks to predict software defects with cost in mind. When evaluated on four NASA datasets, he found that threshold moving algorithm gave the best results in the sole Normalized Expected Cost of Misclassification (NECM) measure. He especially recommended threshold-moving algorithms on projects written in object oriented languages.

@@

\section{Data Sources}
The choice of dataset is extremely important, especially when doing software defect prediction research. Datasets should be representative of actual software projects and should ideally be accessible to the public so the results can be re-tested and verified by others. Within the referenced papers, we found a variety of data sources which we feel need to be discussed. Primarily, we found open-source datasets, NASA datasets, and Windows Vista datasets. We will discuss each along with some reasons why they may have been chosen.
\subsection{Open-source}
\subsection{NASA}
A few papers (Zheng \cite{zheng2010}...) used datasets from NASA. Among them were KC1, used for storage management, KC2, used for scientific data processing, CM1, used for NASA spacecraft instruments, and PC1, used for flight software.

One major possibility for using NASA datasets is that most of their software is critical. A malfunction or crash due to a software defect is not only costly, but can also be deadly. NASA's software needs to be thoroughly tested and bug-fixed before it is ready for use. NASA's datasets contain code metrics and defect information, which is easy to mine and create training and test data from.

NASA datasets are also publicly available. Researchers can more easily verify the results obtained in a study. Also, since these datasets are static, they can be used as a baseline to compare the results from a newly created model against those from other studies.
\subsection{Windows Vista}
